Scalar on Function Regression

### 2022-01-04 Presentation/slides.tex
Plot_generator for PCA

	\begin{frame}{Theory}
		Jakob
		\begin{itemize}
			\item Random function represented as linear combination of basis functions
			\item Just transform to multiple linear regression setting
			\item You already know that from the beginning
		\end{itemize}
	\end{frame}

@@

	\begin{frame}{Estimation via Basis Representation}
		$$Z_j(\omega) = \int_{0}^{1} F(\omega)(s) b_j(s)\mathrm{d}s$$ 
		This is a scalar random variable for which we can calculate a realization for each observation $f_i(t)$ and for each deterministic basis function $b_j(t)$.
		$$Z_{i,j} = \int_{0}^{1} f_i(s) b_j(s)\mathrm{d}s$$
		Leading to the following transformation
		$$Y(\omega) = \alpha + \sum_{j = 1}^{\infty} \psi_j Z_j(\omega) + \epsilon(\omega)$$

>>>>

	\begin{frame}{Theory}
		Jakob
		\begin{itemize}
			\item Random function represented as linear combination of basis functions $\checkmark$
			\item Just transform to multiple linear regression setting $\checkmark$
			\item You already know that from the beginning $\checkmark$
		\end{itemize}
	\end{frame}

@@

	\begin{frame}{Estimation via Basis Representation}
		$$Z_j(\omega) = \int_{0}^{1} F(\omega)(s) b_j(s)\mathrm{d}s$$ 
		This is a scalar random variable leading to the following transformation
		$$Y(\omega) = \alpha + \sum_{j = 1}^{\infty} \psi_j Z_j(\omega) + \epsilon(\omega)$$
		Each combination of observation $f_i(t)$ and deterministic basis function $b_j(t)$ effectively gives us a realization of this random variable.
		$$Z_{i,j} = \int_{0}^{1} f_i(s) b_j(s)\mathrm{d}s$$
